VM-Centric Snapshot Deduplication with Fault Isolation for Converged Cloud Architectures

### 2014-07-17 snapshot_system/paper_background.tex
ref

File backup systems have been developed to use fingerprints generated for
data ``chunks''  to identify duplicate
content~\cite{venti02,Rhea2008}.  In a simple implementation,
it is expensive to compare a large number of 
fingerprints
so several techniques have been proposed to improve duplicate identification. 
For example, the data domain method ~\cite{bottleneck08} 
uses  an in-memory Bloom filter and a prefetching cache for data chunks 
which may be accessed.  
%An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
%Approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
%to reduce memory requirements at the cost of some loss of deduplication
%efficiency.
Additional inline deduplication and  approximation techniques
are studied in ~\cite{extreme_binning09,Guo2011,sparseindex09,Guo2011,Srinivasan2012,WeiZhangIEEE}.  
%and a parallel batch solution for cluster-based deduplication is 
%studied in ~\cite{WeiZhangIEEE}. 
\comments{
All of the above approaches have focused on optimization of deduplication
efficiency or speed, and none of them have considered the impact
of deduplication on fault resilience in a cloud environment.  To do so, we
examine the following properties of VM snapshot deduplication for converged
IaaS architectures.
}
%considered in this paper.
%Our consideration is discussed below.
%VM dependence minimization during deduplication and file system block management.
Even with these optimization and approximation techniques, resource usage such as memory  for deduplication
is still extensive for a shared cloud cluster.  
\comments{
For example, the
sampled index with prefetching, proposed  by Guo and Efstathopoulos\cite{Guo2011},
uses 5GB memory space for 100TB of raw data even the compressed data size
is about 5TB. It is fairly typical for
a physical machine with terabytes of disk storage and tens of gigabytes of memory
to support  more than 20 VMs and 10 snapshots per VM and can require  over 100TB of raw space
even the actual storage space need is about 5TB assuming 20:1 compression ratio with deduplication.
It is not easy  to adopt the sampled index method  for a distributed architecture
and every deduplication request may access a remote machine for index lookup and the overall overhead of access latency 
for all requests can be significant. 
 In general
with a cluster of machines in a cloud cluster, there will be more memory requirement per machine such as a 
fingerprint cache, for cross-machine fingerprint comparison~\cite{bottleneck08,Dong2011} and a deduplication
task often needs several gigabytpes of memory, which impacts other cloud services sharing the computing resource.
}

>>>>

File backup systems have been developed to use fingerprints generated for
data ``chunks''  to identify duplicate
content~\cite{venti02,Rhea2008}.  In a simple implementation,
it is expensive to compare a large number of 
fingerprints
so several techniques have been proposed to improve duplicate identification. 
For example, the data domain method ~\cite{bottleneck08} 
uses  an in-memory Bloom filter and a prefetching cache for data chunks 
which may be accessed.  
%An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
%Approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
%to reduce memory requirements at the cost of some loss of deduplication
%efficiency.
Additional inline deduplication and  approximation techniques
are studied in ~\cite{extreme_binning09,Guo2011,sparseindex09,Guo2011,Srinivasan2012,WeiZhangIEEE}.  
%and a parallel batch solution for cluster-based deduplication is 
%studied in ~\cite{WeiZhangIEEE}. 
\comments{
All of the above approaches have focused on optimization of deduplication
efficiency or speed, and none of them have considered the impact
of deduplication on fault resilience in a cloud environment.  To do so, we
examine the following properties of VM snapshot deduplication for converged
IaaS architectures.
}
%considered in this paper.
%Our consideration is discussed below.
%VM dependence minimization during deduplication and file system block management.
Even with these optimization and approximation techniques, resource usage such as memory  for deduplication
is still extensive for a shared cloud cluster.  
For example, in the experiment discussed in Section~\ref{sect:dedup}, 
cross-machine fingerprint comparison using Bloom filter and approximated routing~\cite{bottleneck08,Dong2011} 
still needs several gigabytes of memory per machine, which impacts other cloud services sharing the same
computing resource while our objective is to have an approximation scheme 
which uses about 100 or few hundred megabytes of memory.

\comments{
For example, the
sampled index with prefetching, proposed  by Guo and Efstathopoulos\cite{Guo2011},
uses 5GB memory space for 100TB of raw data even the compressed data size
is about 5TB. It is fairly typical for
a physical machine with terabytes of disk storage and tens of gigabytes of memory
to support  more than 20 VMs and 10 snapshots per VM and can require  over 100TB of raw space
even the actual storage space need is about 5TB assuming 20:1 compression ratio with deduplication.
It is not easy  to adopt the sampled index method  for a distributed architecture
and every deduplication request may access a remote machine for index lookup and the overall overhead of access latency 
for all requests can be significant. 
 In general
with a cluster of machines in a cloud cluster, there will be more memory requirement per machine such as a 
fingerprint cache, for cross-machine fingerprint comparison~\cite{bottleneck08,Dong2011} and a deduplication
task often needs several gigabytpes of memory, which impacts other cloud services sharing the computing resource.
}
